---
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(daniomotion)

knitr::opts_chunk$set(echo = FALSE, 
                      warning=FALSE, 
                      message=FALSE, 
                      fig.width=10, 
                      fig.height=11)
```


```{r}

# -----------------------------------
# DIRECTIONS
# -----------------------------------

# 1. Specify the path to the directory holding your results files (the 'by_ms.csv' and the 'one_row.csv' files).

  data_dir    <- "./DLC_test_results" 


# 2. Specify the path to a new directory that will hold the compiled results. IMPORTANT: This directory must exist.

  results_dir <- "./final_dfs"
 
  
# 3. Specify the path to the metadata .csv file. 
  
  metadata_file <- "metadata/230202_metadata.csv" 

  
# 4. Give a name to your project.
  
  project <- "test_trial"
  
  
# 5. knit this Rmd.

```



```{r}

dm_aggregrate(project, data_dir, results_dir, metadata_file)

```


# Three data frames, in .csv format, have been generated and saved to the results directory you specified. Each dataframe contains a time stamp consisting of todays date in the following format: YYMMDD.

<br>

#### The **'by_ms_YYMMDD.csv'** consists of the kinematics of each fish on a ms-by-ms basis. It is used if you want to plot the *response* of a fish for a trial, for instance the distance covered every ms by a fish on a given trial (video).

<br>

#### The **'by_trials_YYMMDD.csv'** consists of the overall kinematic variables and kinematic variables broken down by stage. Variables are presented for each trial of each fish. This df is used if you want to check the trial-to-trial repreatability of a kinematic variable. 

<br>

#### The **'fish_means_YYMMDD.csv'** is the 'by_trials.csv' data collapsed across trials into a mean value for each fish. Each fish is therefore represented by a single row in the df, with the kinematic variables representing the mean of the trials. The majority of your statistical analysis will most likely use this dataframe.






